%%%%%%%%%%%%%%%%%
% This is an sample CV template created using altacv.cls
% (v1.1.5, 1 December 2018) written by LianTze Lim (liantze@gmail.com). Now compiles with pdfLaTeX, XeLaTeX and LuaLaTeX.
%
%% It may be distributed and/or modified under the
%% conditions of the LaTeX Project Public License, either version 1.3
%% of this license or (at your option) any later version.
%% The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.3 or later is part of all distributions of LaTeX
%% version 2003/12/01 or later.
%%%%%%%%%%%%%%%%

%% If you need to pass whatever options to xcolor
\PassOptionsToPackage{dvipsnames}{xcolor}
\PassOptionsToPackage{lowtilde}{url}

%% If you are using \orcid or academicons
%% icons, make sure you have the academicons
%% option here, and compile with XeLaTeX
%% or LuaLaTeX.
% \documentclass[10pt,a4paper,academicons]{altacv}

%% Use the "normalphoto" option if you want a normal photo instead of cropped to a circle
% \documentclass[10pt,a4paper,normalphoto]{altacv}

\documentclass[8pt,a4paper,ragged2e, normalphoto]{altacv-dean}

%% AltaCV uses the fontawesome and academicon fonts
%% and packages.
%% See texdoc.net/pkg/fontawecome and http://texdoc.net/pkg/academicons for full list of symbols. You MUST compile with XeLaTeX or LuaLaTeX if you want to use academicons.

% Change the page layout if you need to
\geometry{left=1cm,right=9cm,marginparwidth=6.8cm,marginparsep=1.2cm,top=1.25cm,bottom=1.25cm}

% Change the font if you want to, depending on whether
% you're using pdflatex or xelatex/lualatex
\ifxetexorluatex
  % If using xelatex or lualatex:
  \setmainfont{Carlito}
\else
  % If using pdflatex:
  \usepackage[utf8]{inputenc}
  \usepackage[T1]{fontenc}
  \usepackage[default]{lato}
\fi

% Change the colours if you want to
\definecolor{IFBlue}{HTML}{0F6688}
\definecolor{IFDarkBlue}{HTML}{00425C}
\definecolor{IFMediumBlue}{HTML}{17739A}
\definecolor{IFLightBlue}{HTML}{228FBD}

\definecolor{IFGrey}{HTML}{6D6E71}
\definecolor{IFDarkGrey}{HTML}{231F20}
\definecolor{IFMediumGrey}{HTML}{4D4D4F}
\definecolor{IFLightGrey}{HTML}{808285}

\colorlet{heading}{IFBlue}
\colorlet{accent}{IFLightBlue}
\colorlet{emphasis}{IFMediumGrey}
\colorlet{body}{IFGrey}

% Change the bullets for itemize and rating marker
% for \cvskill if you want to
\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}

%% sample.bib contains your publications
\addbibresource{pubs.bib}

\begin{document}
\name{Dean Lynch}
\tagline{Software Engineer}
% \photo{2.8cm}{filename}
\personalinfo{%
  \email{[REDACTED]}
  \phone{[REDACTED]}
  \location{Dublin, Ireland}
  \linkedin{in/deanlynch97}
  \github{github.com/lynchdean}
  \homepage{deanlynch.xyz}
}

%% Make the header extend all the way to the right, if you want.
\begin{fullwidth}
\makecvheader

\cvsection{Profile}
\begin{flushleft}
    I am currently working as a Software Test Engineer in the telecommunications industry, developing SMS firewall solutions. 
    Graduated from Dublin City University, with a BSc. in Computer Applications \& Software Engineering. Seeking a Software Engineering role in an environment in which I can apply my skills and challenge myself, as well as learn and gain experience.
\end{flushleft}

\cvsection{Experience}
    \cvevent{Software Engineer}{Anam Technologies}{September 2021 - Present}{Dublin}{}{}

    \divider

    \cvevent{Software Test Engineer}{Anam Technologies}{March 2021 - September 2021}{Dublin}{}{}
    \begin{itemize}
        \item Conducting automation testing using Jenkins for latest product candidates.
        \item Conducting performance/load testing using internal test tool for latest product candidates.
        \item Monitoring, troubleshooting and reporting of bugs and defects to Bugzilla.
        \item Carried out testing of AWS hosted implementation for troubleshooting and to assess viability. 
        \item Optimisation of established testing processes and scripts.
    \end{itemize}
    \divider
    
    \cvevent{Software Engineering Intern}{Bloomberg PolarLake}{April 2018 -- September 2018}{Dublin}{}{}
    \begin{itemize}
        \item Successfully developed a query service controller and user interface using Java and Angular 6.
        \item Investigated and implemented Apache Cassandra with an existing file store.
        \item Carried out performance testing using Gatling for a new service API, and documented the results at each stage of development.
        \item Generated graphs and reports from various JSON input using Python, Java, Kibana.
        \item Bug fixing and improvements to business logic.
    \end{itemize}
    \divider

\end{fullwidth}

\cvsection[sidebar]{Education}
    \cvevent{BSc. in Computer Applications \& Software Engineering}{Dublin City University}{2015 -- 2019}{Dublin}{}{}
    
    \divider
    
    \cvevent{Leaving Certificate}{St. Josephs Secondary School}{2009 -- 2015}{Rush, Co. Dublin}{}{}


\cvsection{Projects}
    \cvevent{Password Manager with P2P Synchronisation}{Final Year Project}{2019}{}{}{}
    \begin{itemize}
        \item A cross-platform desktop application using a locally stored KeePass database.
        \item Integrated P2P database synchronisation.
        \item Technologies: \cvtag{Java} \cvtag{JavaFx} \cvtag{KeePass}
    \end{itemize}
    \divider

    \cvevent{Freelance Web Application using Ethereum Blockchain}{Third Year project (Pair)}{2018}{}{}{}
    \begin{itemize}
        \item  A modern web application for people seeking or providing freelance work.
        \item All accounts and transactions stored using smart contracts on the Etherium blockchain.
        \item Technologies: \cvtag{JavaScript} \cvtag{Solidity} \cvtag{AngularJS} \cvtag{web3.js}
    \end{itemize}
    
\begin{fullwidth}
    \divider
    
    \cvevent{Product Finder \& Automated Checkout tool}{Personal Project}{2017}{}{}{}
    \begin{itemize}
        \item A web scraping tool to find the product page of a product on a specified website.
        \item Automatic check-out and configurable auto-fill using a selenium driven web browser.
        \item Technologies: \cvtag{Python} \cvtag{Selenium} \cvtag{Beautiful Soup}
    \end{itemize}
    \divider
    
    \cvevent{Bird Watch Fingal Website}{bwifingal.ie}{2021}{}{}{}
    \begin{itemize}
        \item Modern and responsive website built for the Bird Watch Ireland Fingal branch.
        \item Technologies: \cvtag{React} \cvtag{TypeScript} \cvtag{Bootstrap}
    \end{itemize}

\end{fullwidth}

\end{document}
